---
title: "STAT 413 Data Science Homework 2"
author: "Hyo Young Ana Lim"
date: "2/17/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1) Enter and run USArrests. What type of information is shown in the data table USArrests?  (Three or four sentences)

```{r}
USArrests
```
USArrests contains statistics in arrests made in different states for murder, assault, and rape. It is also showing the percentage of urban population in each state. 

2) Use and show R coding that features a map function to show maximum values for all variables of the USArerests data frame.  Which State has the largest number of Assaults according to the USAressts data frame?

```{r}
library(tidyverse)
pmap_dbl(USArrests, max)
```

3) Install the nycflights13 package: install.packages("nycflights13") , call the following library:  library(nycflights13), and then enter flights (this will produce the flights data table)

```{r}
library(nycflights13)
flights
```

4) Use and show R code that will indicate how many rows and how many columns the flights data has.  Review and revisit your notes from STAT 412/612.  Describe a tibble (two or three sentences). Now use and show R code that verifies that flights is a tibble

```{r}
nrow(flights)
ncol(flights)
```

5) Now Use and show R code (featuring a map function) that will output the type of each column of the flights tibble.

```{r}
map(flights, typeof)
```

6)  Use and show R coding that features usage of a map function to find the slope and the intercept of models for the different levels of the Species variable of the iris data frame.  For each model, Sepal.Width predicts Sepal.Length.

```{r}
model1 <- iris %>%
  split(.$Species) %>%
  map(~lm(Sepal.Length ~ Sepal.Width, data = .))
model1
```

7)
```{r}
V <- list(12, 22, 27, 31.5, NA, 39, "east")
V
```

For the given list above;
7a) Use and show R code to find the length of the list
```{r}
length(V)
```

7b) Use and show R code that will extract the missing value
```{r}
V[is.na(V)]
```

7c) Use and show R code that will extract the third object
```{r}
V[3]
```

7d) Use and show R code that will extract the character string and the minimum number.
```{r}
V[c(1,7)]
```

7e) Use one line of code to show that the seventh object is a character object.
```{r}
str(V[7])
```
